Thermodynamic fragments in magic state theories

### 2020-11-19 magic_paper.tex
Indices cleanup

We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
\begin{align}
    &{\W{\noisysn}} = \\ 
    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
    &\left\{ \left( 8^{n-2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
\end{align}

@@

Consider now the state 
\begin{equation}
    \rho(m, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes m} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
\end{equation}

Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
The new point coordinates are given by:
\begin{align}
    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \\
    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \\
    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
    &\text{for } k=0,\dots,\frac{n}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
\end{align}

We can unify the indices, by introducing a single index
\begin{equation}
    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{m-2j}\binom{m}{2j} \right]9^s,
\end{equation}
so that $i=1,2,\dots, \frac{1}{2}(7^{m+s} + 9^{m+s})$.
The $\frac{m}{2}$ elbows correspond to $\beta=0,\ \alpha=1$.
This index function is bijective.

@@

Consider the Strange state purification process in the unital fragment,
\begin{equation}\label{eq:su_conversion}
    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(m, \epsilon', s).
\end{equation}
In order to get Lorenz curve constraints on this state conversion, we need to match up the indices for the two states.
We use non-primed indices for the initial state and primed indices for the target state,
\begin{align}
    i(k, \alpha) &= (\alpha-1) + \sum_{j=0}^{k-1} 8^{n-2j}\binom{n}{2j}, \\
    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{m-2j'}\binom{m}{2j'} \right]9^s,
\end{align}

The question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}

@@

	Let $k$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_k, x_{k+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{k+1} = 1$.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $k =0,\dots,n+1$.

	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,k$.
	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{k+1}) = \lc{\tau}{\sigma}(x_{k+1}) = 1$.

@@

	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,k$, so the proof is complete.
\end{proof}

Returning to~\cref{eq:su_conversion}, the $k$ independent necessary constraints are
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_{1,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{1,0,0}), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_{2,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{2,0,0}), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_{m,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{m,0,0}), \nonumber
\end{align}
where $x_{1,0,0}, x_{2,0,0}, \dots, x_{m,0,0} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

>>>>

We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
\begin{align}
    &{\W{\noisysn}} = \\ 
    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
    &\left\{ \left( 8^{2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
\end{align}

@@

Consider now the state 
\begin{equation}
    \rho(r, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes r} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
\end{equation}

Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
The new point coordinates are given by:
\begin{align}
    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \\
    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \\
    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
    &\text{for } k=0,\dots,\frac{r}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
\end{align}

We can unify the indices, by introducing a single index
\begin{equation}
    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{r}{2j} \right]9^s,
\end{equation}
so that $i=1,2,\dots, \frac{1}{2}9^s(7^{r} + 9^{r})$.
The $\frac{r}{2}$ elbows correspond to 
\begin{equation}
	i(k, \alpha, \beta) = i(\kappa, m_{\kappa}, 9^s) \equiv \sum_{j=0}^{\kappa} m_j,\ \kappa = 0,\dots,\frac{r}{2}.
\end{equation}
This index function is bijective.

@@

Consider the Strange state purification process in the unital fragment,
\begin{equation}\label{eq:su_conversion}
    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(r, \epsilon', s),\ n = r + s.
\end{equation}
In order to get Lorenz curve constraints on this state conversion, we need to match up the indices for the two states.
We use non-primed indices for the initial state and primed indices for the target state,
\begin{align}
    i(k, \alpha) &= 1 + (\alpha-1) + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j}, \\
    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{2j'}\binom{r}{2j'} \right]9^s,
\end{align}
for $i,i' = 1,2,\dots, \frac{1}{2}(7^{n} + 9^{n})$.

We need $x_{i(k, \alpha)} = x_{i'(k', \alpha', \beta')}$, so the question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}

In other words, we choose a fixed $i'(k',\alpha',\beta')$ and we are searching for $i(k, \alpha)$ such that 
\begin{equation}
	i(k, \alpha) \equiv \alpha + \sum_{j=0}^{k-1} 8^{2j}\binom{n}{2j} = i'(k',\alpha',\beta').
\end{equation}

As an example, consider the process 
\begin{equation}
\rho_{\rm{S}}(\epsilon)^{\otimes 4} \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(\epsilon')^{\otimes 2} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2}.
\end{equation}
We want to check which Lorenz curve is higher at the first two elbows of the target state, i.e. we want to verify or reject the inequalities
\begin{align}
	L_{i(k_0, \alpha_0)} &\geq L_{i'(0, 1, 81)}, \\
	L_{i(k_1, \alpha_1)} &\geq L_{i'(1, 64, 81)},
\end{align}
where the first two multiplicities of the target state are $1$ and $64$.
The challenge is to find $k_0, \alpha_0$ such that $i(k_0, \alpha_0) = i'(0,1,81)$ and $k_1, \alpha_1$ such that $i(k_1, \alpha_1) = i'(1,64,81)$

@@

	Let $r$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_r, x_{r+1} \}$ be the $x$-coordinates of the elbows with $x_0 = 0$ and $x_{r+1} = 1$.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.

	Conversely, assume that $\lc{\rho}{\sigma}(x_j) \geq \lc{\tau}{\sigma}(x_j)$ for all $j =1,\dots,r$.
	First, note that $\lc{\rho}{\sigma}(x_0) = \lc{\tau}{\sigma}(x_0) = 0$ and $\lc{\rho}{\sigma}(x_{r+1}) = \lc{\tau}{\sigma}(x_{r+1}) = 1$.

@@

	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,r$, so the proof is complete.
\end{proof}

Returning to~\cref{eq:su_conversion}, the $r$ independent necessary constraints are
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(0, m'_{0}, 9^{s})}\right), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(1, m'_{1}, 9^{s})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}\left(x_{(r, m'_{r}, 9^{s})}\right), \nonumber
\end{align}
where $x_{(0, m'_{0}, 9^{s'})}, x_{(1, m'_{1}, 9^{s'})}, \dots, x_{(r, m'_{r}, 9^{s'})} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

\null\newpage
\null\newpage
